This paper introduces a Multi-Account and Multi-Tenant Policy-Based Access Control (PBAC) approach for distributed systems, formalized through the use of relational structures, relational algebra and operations.
The approach is further enhanced by generating risk scores.
As cloud computing became more prevalent, there was a growing demand for sophisticated software solutions, especially in Software as a Service (SaaS) offerings.
These systems effectively handle data across diverse accounts, tenants, computing nodes, and networks.
This approach introduces various problems. (1) First and foremost, permissions must be expressed in a straightforward manner to implement both Role-Based Access Control (RBAC) and Attribute-Based Access Control (ABAC).
(2) Secondly, the approach necessitates low-latency and high-availability for the evaluation of permissions.
This becomes particularly intricate due to the inherent challenges posed by the PACELC theorem. Furthermore, in a distributed system with asynchronous operations, there is no assurance that the permissions initially allowing the action remain valid at execution time.
It is crucial to mitigate this risk and maximize the likelihood of executing with the latest valid permissions at the time of execution.
(3) Finally, risk assessment becomes intricate, especially as policies granting permissions grow complex. The approach must be capable of handling the complexity of these policies and effectively assess the associated risks.

To address these problems, this paper introduces an architecture, relations, algorithms and an approach for generating risk classifications using scores.
